---
title: "protein_paper_plots"
author: "Heather Wheeler"
date: "`r Sys.time()`"
output: html_document
---

Ryan's directories on ROCKS hsdbc1

- INTERVAL prediction

`/home/rschubert1/scratch/TOPMed_Proteome/10INTERVAL_prediction/double_dipped_correlation`

- MESA models

`/home/rschubert1/data/TOPMED_Proteome/*/PCAIR_modeling/06Elastic_net/dbs_out/*rho0.1_zpval0.05.db`

To make rho_avg txt files from command line:
```
sqlite3 CAU_PCAIR_baseline_models_unfiltered.db
.headers on
.mode tabs
.output rho_avg_values_EUR_PCAIR_baseline_models.txt
select gene, genename, rho_avg, [pred.perf.pval] from extra;
.quit
```

**Needed input files are in `/home/wheelerlab3/topmed/protein_paper_plots/`**

### rho_avg ditributions
```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(viridisLite)
library(ggridges)
library(gridExtra)
library(cowplot)
"%&%" = function(a,b) paste(a,b,sep="")

for(pop in c("ALL", "AFA", "CHN", "EUR", "HIS")){
  bl <- fread("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/wheeler_figures/rho_avg_values_" %&% pop %&% "_PCAIR_baseline_models.txt") %>% mutate(pop=pop, model="baseline")
  if(exists('res')){
    res <- rbind(res, bl)
  }else{
    res <- bl
  }
  fm <- fread("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/wheeler_figures/rho_avg_values_" %&% pop %&% "_PCAIR_dapg_0.001_T.txt") %>% mutate(pop=pop, model="fine-mapped")
    res <- rbind(res, fm)
}

#order pops by sample size
res <- mutate(res,pop=factor(pop,levels=c('ALL','EUR','HIS','AFA','CHN')))

a<-ggplot(res, aes(x=rho_avg, y=pop, fill=model, color=model)) + geom_density_ridges(alpha=0.1) +
  scale_color_viridis_d(begin=0.7,end=0) + scale_fill_viridis_d(begin=0.7,end=0) + theme_bw(12) +
  xlab(expression("model performance" ~ rho)) + ylab("population") + geom_vline(xintercept=0.1,linetype = "dashed") +
  ggtitle("A")
print(a)

res0.1 <- filter(res, rho_avg>0.1)
#ggplot(res0.1, aes(x=rho_avg, y=pop, fill=model, color=model)) + geom_density_ridges(alpha=0.4) +
#  scale_color_viridis_d(begin=0.7,end=0) + scale_fill_viridis_d(begin=0.7,end=0) + theme_ridges()

res0.1_p <- filter(res, rho_avg>0.1, pred.perf.pval<0.05)
#ggplot(res0.1_p, aes(x=rho_avg, y=pop, fill=model, color=model)) + geom_density_ridges(alpha=0.4) +
#  scale_color_viridis_d(begin=0.7,end=0) + scale_fill_viridis_d(begin=0.7,end=0) + theme_ridges()
```

### Protein model counts by sample size
```{r,fig.width=5,fig.height=5}
counts <- fread('Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/wheeler_figures/protein_counts.txt')
counts <- mutate(counts, n=c(183,183,71,71,416,416,301,301,971,971))
b<-ggplot(counts,aes(x=n,y=count,color=model,fill=model)) + geom_point() + 
  geom_label(aes(label=pop),nudge_y=-45,alpha=0.1,size=2) + 
  scale_color_viridis_d(begin=0,end=0.7,name = "Model", labels = c("fine-mapped","baseline")) + theme_bw(12) + 
  scale_fill_viridis_d(begin=0,end=0.7,name = "Model", labels = c("fine-mapped","baseline")) +
  theme(legend.position = "none") +
  xlab("population size") + ylab(expression("protein model count ("*rho>0.1*")")) + coord_cartesian(ylim=c(0,600), xlim=c(0,1000)) + ggtitle("B")
print(b)
```

```{r,fig.height=5, fig.width=12}

fig1 <- plot_grid(a,b,align="h",rel_widths = c(0.58,0.42))
print(fig1)
tiff("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig1.tiff", width = 19, height = 8, units = 'cm', res = 300, compression = 'lzw')
fig1
dev.off()

png("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig1.png", width = 19, height =8, units = 'cm', res = 300)
fig1
dev.off()

fig1 + ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig1.pdf", width = 19, height = 8, units = 'cm', dpi = 300)
```

### compare model performance in INTERVAL
```{r}
for(pop in c("ALL", "AFA", "CHN", "EUR", "HIS")){
  bl <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_baseline_models_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="baseline")
  fm <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_dapg_0.001_T_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="fine-mapped")
  #filter to intersection proteins
  bl <- filter(bl, gene_id %in% fm$gene_id)
  fm <- filter(fm, gene_id %in% bl$gene_id)
  if(exists('intres')){
    intres <- rbind(intres, bl)
  }else{
    intres <- bl
  }
  intres <- rbind(intres, fm)
}

cat("# proteins per pop")
print(filter(intres,model=="baseline") %>% count(pop))

ggplot(intres, aes(x=model,y=estimate,col=model)) + geom_violin() + geom_boxplot(width=0.25) +
  facet_wrap(~pop) + scale_color_viridis_d(begin=0.7,end=0) + theme_bw() + theme(legend.position = "none") +
  xlab("Model") + ylab(expression("INTERVAL"~rho))
#to do: add stats

#actually, paired test (by protein w/in pop) works best, thanks Ryan!
for(pop in c("ALL", "AFA", "CHN", "EUR", "HIS")){
  bl <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_baseline_models_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="baseline")
  fm <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_dapg_0.001_T_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="fine-mapped")
  j <- inner_join(bl,fm,by="gene_id")
  cat(pop)
  print(wilcox.test(j$estimate.x,j$estimate.y,paired=TRUE))
  print(t.test(j$estimate.x,j$estimate.y,paired=TRUE))
}
```

### Compare ALL v. EUR performance in INTERVAL
```{r}
pop="ALL"
allbl <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_baseline_models_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="baseline")
allfm <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_dapg_0.001_T_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="fine-mapped")
dim(allbl)
dim(allfm)
pop="EUR"
eurbl <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_baseline_models_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="baseline")
eurfm <- fread("Z:/scratch/TOPMed_Proteome/10INTERVAL_prediction/true_subset_correlations/" %&% pop %&% "_PCAIR_dapg_0.001_T_rho0.1_zpval0.05_correlation.txt") %>% mutate(pop=pop, model="fine-mapped")
dim(eurbl)
dim(eurfm)
#all pop res
popres <- rbind(allbl,eurbl,allfm,eurfm)
ggplot(popres, aes(y=estimate, x=pop, color=model, fill=model)) + geom_violin(alpha=0.1) + geom_boxplot(width=0.25,fill="white") +
  facet_wrap(~model) + scale_color_viridis_d(begin=0.7,end=0) + scale_fill_viridis_d(begin=0.7,end=0) + theme_bw(14) + 
  theme(legend.position = "none") + xlab("population") + ylab(expression("INTERVAL"~rho))

#intersection pop res
allbl <- filter(allbl, gene_id %in% eurbl$gene_id)
eurbl <- filter(eurbl, gene_id %in% allbl$gene_id)
allfm <- filter(allfm, gene_id %in% eurfm$gene_id)
eurfm <- filter(eurfm, gene_id %in% allfm$gene_id)
dim(allbl)
dim(allfm)
dim(eurbl)
dim(eurfm)

popres <- rbind(allbl,eurbl,allfm,eurfm)

fig3<-ggplot(popres, aes(y=estimate, x=pop, color=model, fill=model)) + geom_violin(alpha=0.1) + geom_boxplot(width=0.25,fill="white") +
  facet_wrap(~model) + scale_color_viridis_d(begin=0.7,end=0) + scale_fill_viridis_d(begin=0.7,end=0) + theme_bw(14) + 
  theme(legend.position = "none") + xlab("population") + ylab(expression("INTERVAL"~rho)) + ggtitle("A")
print(fig3)
tiff("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3.tiff", width = 19, height = 9.5, units = 'cm', res = 300, compression = 'lzw')
fig3
dev.off()
png("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3.png", width = 19, height = 9.5, units = 'cm', res = 300)
fig3
dev.off()

#paired wilcox test
bl <- inner_join(allbl,eurbl,by="gene_id")
fm <- inner_join(allfm,eurfm,by="gene_id")
cat("Baseline")
print(wilcox.test(bl$estimate.x,bl$estimate.y,paired=TRUE))
print(t.test(bl$estimate.x,bl$estimate.y,paired=TRUE))
cat("Fine-mapped")
print(wilcox.test(fm$estimate.x,fm$estimate.y,paired=TRUE))
print(t.test(fm$estimate.x,fm$estimate.y,paired=TRUE))

#make scatter plot ALL vs. EUR stratified by model
blfm <- rbind(bl,fm)
fig3alt<- ggplot(blfm, aes(x=estimate.y, y=estimate.x)) + geom_point() + facet_wrap(~model.x) + geom_abline(slope=1,intercept=0) + geom_density_2d() +
  xlab(expression("INTERVAL"~rho*" (EUR training)")) + ylab(expression("INTERVAL"~rho*"  (ALL training)")) +theme_bw(14) +  coord_cartesian(xlim=c(-0.05,1),ylim=c(-0.05,1))+
  ggtitle("B")
print(fig3alt)
tiff("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3alt.tiff", width = 19, height = 9.5, units = 'cm', res = 300, compression = 'lzw')
fig3alt
dev.off()
png("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3alt.png", width = 19, height = 9.5, units = 'cm', res = 300)
fig3alt
dev.off()
```

```{r,fig.height=6,fig.width=6}
fig3ab <- plot_grid(fig3,fig3alt,nrow=2)
print(fig3ab)
tiff("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3ab.tiff", width = 18, height = 19, units = 'cm', res = 300, compression = 'lzw')
fig3ab
dev.off()
png("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3ab.png", width = 18, height = 19, units = 'cm', res = 300)
fig3ab
dev.off()
fig3ab + ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/Fig3ab.pdf", width = 18, height = 19, units = 'cm', dpi = 300)


```
