---
title: "check replication"
author: "Ryan Schubert"
date: "April 5, 2021"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(dplyr)
library(ggplot2)
library(stringr)
library(viridis)
library(RSQLite)
library(cowplot)
"%&%" = function(a,b) paste(a,b,sep="")
```

## now count how many hits replicate from PAGE into UKBB+

how many page spred hits are ukbb spred hits
how many page spred+coloc hits are ukbb spred hits
how many page spred+coloc hits are ukbb spred+coloc hits

```{r}
filemap<-fread("Z:/data/ukbb_sum_stats/pheno_summary/phenotype_to_filename_map.csv",header=F)
filemap<-filemap %>% 
  mutate(V2=gsub("\\.gz","",V2),
         V2=gsub("\\.bgz","",V2),
         V2=gsub("\\.tsv","",V2),
         V2=gsub("\\.csv","",V2),
         V2=gsub("\\.txt","",V2),
         V2=gsub("\\.hg38","",V2),
         V2=gsub("\\.hs38","",V2),
         V2=gsub("\\.dbgap","",V2))
colnames(filemap)<-c("Phenotype","gwas_file")

page_all_spred_dir<-"Z:/scratch/test_coloc_for_elyse/SPred_results/all_results/"
ukbb_all_spred_dir<-"Z:/data/ukbb_sum_stats/spred_out/"
model_vec<-c("baseline","dapg_0.001_F","dapg_0.001_T","dapg_0.01_F","dapg_0.01_T","dapg_0_F","dapg_0_T")
#
pav_vec<-c(F)
model_list<-expand.grid(model_vec,pav_vec,stringsAsFactors = F)

model_comparisons_list=vector(mode="list",nrow(model_list))

#at each model level check replication in either direction
for (m in 1:nrow(model_list)){
  model_actual<-model_list[m,1]
  pav<-model_list[m,2]
  
  #read in ukbb resuts for this model level
  ukbb_spred_files<-list.files(ukbb_all_spred_dir,pattern=model_actual)
  if (pav == T){
    ukbb_spred_files<-ukbb_spred_files[grepl("PAV_filtered",ukbb_spred_files) & !grepl("csv",ukbb_spred_files)]
  } else {
    ukbb_spred_files<-ukbb_spred_files[!grepl("PAV_filtered",ukbb_spred_files) & !grepl("csv",ukbb_spred_files)]
  }
  ukbb_spred_list<-vector(mode="list",length(ukbb_spred_files))
  for (f in 1:length(ukbb_spred_files)){
    ukbb_spred_list[[f]]<-fread(ukbb_all_spred_dir %&% ukbb_spred_files[f]) %>% mutate(source=ukbb_spred_files[f])
  }
  ukbb_spred_list<-ukbb_spred_list[lapply(ukbb_spred_list,nrow)>0]
  ukbb_spred_results<-bind_rows(ukbb_spred_list) %>%
    mutate(model=str_extract(source,"[A-Z]+_PCAIR_[:graph:]+_rho0.1_zpval0.05"),
           gwas_file=str_remove(source,"_Spred_[A-Z]+_PCAIR_[:graph:]+_rho0.1_zpval0.05"),
           gwas_file=gsub("\\.hg38","",gwas_file),
           gwas_file=gsub("\\.hs38","",gwas_file),
           gwas_file=gsub("\\.dbgap","",gwas_file),
           train_pop=substr(model,1,3),
           PAV_filtered=if_else(grepl("PAV_filtered",model),"TRUE","FALSE"),
           model=gsub("_PAV_filtered","",model),
           model=gsub("[A-Z]+_PCAIR_","",model),
           model=gsub("_rho0.1_zpval0.05","",model),
           model=gsub("_models","",model),
           model=gsub("dapg_","",model),
           gene=gsub("\\.[0-9]+","",gene)) %>%
      inner_join(filemap,by=c("gwas_file"))
  ukbb_spred_results<-ukbb_spred_results %>% 
    mutate(bonf_thresh=0.05/nrow(ukbb_spred_results)) %>%
    select(gene,gene_name,zscore,effect_size,pvalue,var_g,n_snps_used,n_snps_in_model,model,train_pop,PAV_filtered,Phenotype,bonf_thresh) %>%
    rename_with(.fn=function(x){paste("ukbb",x,sep="_")})
  
  #read in page results for this model level
  page_spred_files<-list.files(page_all_spred_dir,pattern=model_actual)
  if (pav == T){
    page_spred_files<-page_spred_files[grepl("PAV_filtered",page_spred_files)]
  } else {
    page_spred_files<-page_spred_files[!grepl("PAV_filtered",page_spred_files)]
  }
  page_spred_results<-fread(page_all_spred_dir %&% page_spred_files)
  page_spred_results<-page_spred_results %>% 
    mutate(bonf_thresh=0.05/nrow(page_spred_results),
           Phenotype=if_else(Phenotype=="LDL_choleseterol","LDL_cholesterol",Phenotype)) %>%
    select(GENE,gene_name,zscore,effect_size,P,var_g,n_snps_used,n_snps_in_model,Model,pred_perf_r2,pred_perf_pval,Phenotype,bonf_thresh) %>%
    rename(train_pop=Model) %>%
    rename_with(.fn=function(x){paste("page",x,sep="_")})
  model_comparisons_list[[m]]<-full_join(page_spred_results,ukbb_spred_results,by=c("page_GENE"="ukbb_gene","page_gene_name"="ukbb_gene_name","page_train_pop"="ukbb_train_pop","page_Phenotype"="ukbb_Phenotype")) %>%
    rename(gene="page_GENE",gene_name="page_gene_name",train_pop="page_train_pop",Phenotype="page_Phenotype",model="ukbb_model",PAV_filtered="ukbb_PAV_filtered") %>%
    mutate(model=model_actual,PAV_filtered=pav)
}
fwrite(bind_rows(model_comparisons_list),"Z:/scratch/TOPMed_Proteome/08PWAS/tmp_all_results.csv")



#how many page spred hits at
#ukbb bonf significant
#page bonf signif
#bonf signif for number of proteins tested for replication

```


```{r}
all_results<-bind_rows(model_comparisons_list)
# all_results<-fread("Z:/scratch/TOPMed_Proteome/08PWAS/tmp_all_results.csv",showProgress = T)
# # cor.test(all_results$page_zscore,all_results$ukbb_zscore,use="complete.obs")
# # ggplot(data=all_results,aes(x=page_zscore,y=ukbb_zscore)) +
# #   geom_point() + 
# #   theme_bw() + 
# #   geom_smooth(method="lm")
# 
# vec1<-unique(page_coloc_results$phenotype) 
# 
# vec2<-unique(all_results$Phenotype)
# sort(vec1) == sort(vec2)
```

```{r}
#read in coloc data
page_coloc_results<-fread("Z:/scratch/TOPMed_Proteome/08PWAS/PAGE_coloc_results.csv") %>% 
  group_by(train_pop,phenotype,gene) %>% 
  slice_max(PP.H4.abf,n=1) %>% 
  ungroup()
ukbb_coloc_results<-fread("Z:/scratch/TOPMed_Proteome/08PWAS/UKBB_coloc_results.csv") %>%
  group_by(train_pop,phenotype,gene) %>% 
  slice_max(PP.H4.abf,n=1) %>% 
  ungroup() %>%
  mutate(gene=gsub("\\.[0-9]+","",gene))


page_bonf_counts<-all_results %>% filter(!is.na(page_zscore),page_P < page_bonf_thresh) %>% count(model,train_pop) %>% mutate(loose_threshold=0.05/n)
ukbb_bonf_counts<-all_results %>% filter(ukbb_pvalue < ukbb_bonf_thresh) %>% count(model,train_pop) %>% mutate(loose_threshold=0.05/n)


(page_spred_count_plot <- all_results %>% 
  filter(page_P < page_bonf_thresh) %>% 
  mutate(model=gsub("dapg_","",model),train_pop=if_else(train_pop=="CAU","EUR",train_pop)) %>%
  count(model,train_pop) %>%
    ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  labs(fill="Training Population") +
  theme_bw() +
    theme(axis.title.x=element_blank()) +
  ylab("N S-PrediXcan\nSignificant") +
  scale_fill_viridis(discrete=T))

(page_spred_count_focused_plot <- all_results %>% 
  filter(page_P < page_bonf_thresh) %>% 
  mutate(model=gsub("dapg_","",model)) %>% 
    filter(model %in% c("baseline","0.001_T")) %>%
    mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop),
           model=if_else(model=="0.001_T","fine-mapped",model)) %>%
  count(model,train_pop) %>%
    ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  labs(fill="Training Population") +
  theme_bw() +
    theme(axis.title.x=element_blank()) +
  ylab("N S-PrediXcan\nSignificant") +
  scale_fill_viridis(discrete=T))

page_discoveries<-all_results %>% 
  inner_join(page_coloc_results,by=c("gene","train_pop","Phenotype"="phenotype")) %>%
  filter(page_P < page_bonf_thresh,PP.H4.abf >0.5) %>% 
  mutate(model=gsub("dapg_","",model)) %>%
  count(model,train_pop)

(page_discoveries_plot<-page_discoveries %>%
    mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop)) %>%
  ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  labs(fill="Training Population") +
  theme_bw() +
    theme(axis.title.x=element_blank()) +
  ylab("N S-PrediXcan &\nCOLOC Significant") +
  scale_fill_viridis(discrete=T))

(page_discoveries_focused_plot<-page_discoveries %>%
      filter(model %in% c("baseline","0.001_T")) %>%
    mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop),
           model=if_else(model=="0.001_T","fine-mapped",model)) %>%
  ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  labs(fill="Training Population") +
  theme_bw() +
    theme(axis.title.x=element_blank()) +
  ylab("N S-PrediXcan &\nCOLOC Significant") +
  scale_fill_viridis(discrete=T))

#how many bonf page hits have the same sign in ukbb, have the ukbb pval meet a strict bonf threshold, and are colocalized in page

page_bonf_colocalized_ukbb_strict<-all_results %>% 
  inner_join(page_bonf_counts,by=c("model","train_pop")) %>% 
  inner_join(page_coloc_results,by=c("gene","train_pop","Phenotype"="phenotype")) %>%
  mutate(model=gsub("dapg_","",model)) %>%
  filter(page_P < page_bonf_thresh, sign(page_zscore) == sign(ukbb_zscore),ukbb_pvalue < ukbb_bonf_thresh,PP.H4.abf > 0.5) %>% 
  count(model,train_pop)

page_results_focused<-page_bonf_colocalized_ukbb_strict %>% 
  filter(model %in% c("0.001_T","baseline")) %>%
  mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop),
         model=if_else(model=="0.001_T","fine-mapped",model)) %>%
  ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  theme_bw() +
  ylab("N Replicated") +
  labs(fill="Training Population") +
  scale_fill_viridis(discrete=T)


page_results<-page_bonf_colocalized_ukbb_strict %>% 
  mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop)) %>%
  ggplot(data=.,aes(x=model,y=n)) +
  geom_col(aes(fill=train_pop),position="dodge") +
  theme_bw() +
  ylab("N Replicated") +
  labs(fill="Training Population") +
  scale_fill_viridis(discrete=T)


legend <- get_legend(
  page_results_focused + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

grid<-plot_grid(page_spred_count_focused_plot + theme(legend.position="none"),
                page_discoveries_focused_plot + theme(legend.position="none"),
                page_results_focused + theme(legend.position="none"),
                labels = c("A","B","C"),
                align="v",
                ncol=1) 
plot_grid(grid,legend,ncol = 1, rel_heights = c(1, .1)) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/PAGE_spred_coloc_rep.pdf",dpi=700,height=7,width=7) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/PAGE_spred_coloc_rep.png",dpi=700,height=7,width=7) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/PAGE_spred_coloc_rep.tiff",dpi=700,height=7,width=7) 

legend <- get_legend(
  page_results + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

grid<-plot_grid(page_spred_count_plot + theme(legend.position="none"),
                page_discoveries_plot + theme(legend.position="none"),
                page_results + theme(legend.position="none"),
                labels = c("A","B","C"),
                align="v",
                ncol=1) 
plot_grid(grid,legend,ncol = 1, rel_heights = c(1, .1)) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/supplemental_PAGE_spred_coloc_rep.pdf",dpi=700,height=7,width=7) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/supplemental_PAGE_spred_coloc_rep.png",dpi=700,height=7,width=7) +
  ggsave("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/supplemental_PAGE_spred_coloc_rep.tiff",dpi=700,height=7,width=7) 
```



```{r}

page_bonf_colocalized_ukbb_strict<-all_results %>%
  inner_join(page_coloc_results,by=c("gene","train_pop","Phenotype"="phenotype")) %>%
  mutate(model=gsub("dapg_","",model)) %>%
  filter(page_P < page_bonf_thresh ,PP.H4.abf > 0.5) %>%
  mutate(replicated=if_else((sign(page_zscore) == sign(ukbb_zscore)) & (ukbb_pvalue < ukbb_bonf_thresh),T,F))

hits<-page_bonf_colocalized_ukbb_strict %>% filter(replicated==T, model %in%c("baseline","0.001_T")) %>% select(gene,Phenotype,replicated) %>% arrange() %>% distinct()

soma_uniprot_map<-fread("Z:/scratch/TOPMed_Proteome/06Elastic_net/PAV_modeling_methods/01PAV_annotation/somascan1.3k_aptamer_info.txt") %>% select(SomaId,TargetFullName,Target,UniProt,EntrezGeneSymbol) %>% arrange() %>% distinct()

library(tidyr)
hits<-hits %>% separate(gene,into=c("SomaId","gene")) %>%
  inner_join(soma_uniprot_map,by=c("SomaId","gene")) %>% arrange(Target)
fwrite(hits,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/annotated_associaitons.csv")
```

create supplemental table 7

```{r}
page_bonf_colocalized_ukbb_strict<-all_results %>%
  inner_join(page_coloc_results,by=c("gene","train_pop","Phenotype"="phenotype")) %>%
  rename(PAGE_PP.H4.abf="PP.H4.abf",pred_perf_r2="page_pred_perf_r2",pred_perf_pval="page_pred_perf_pval") %>% select(-hit1,-hit2,-source) %>%
  full_join(ukbb_coloc_results, by=c("gene","train_pop","Phenotype"="phenotype")) %>%
  rename(ukbb_PP.H4.abf="PP.H4.abf") %>% select(-hit1,-hit2,-source) %>%
  mutate(model=gsub("dapg_","",model)) %>%
  filter(page_P < page_bonf_thresh) %>%
  mutate(replicated=if_else((sign(page_zscore) == sign(ukbb_zscore)) & (ukbb_pvalue < ukbb_bonf_thresh),T,F))


supplemental_table<- page_bonf_colocalized_ukbb_strict %>% select(gene,Phenotype,train_pop,	model,
                                                                  pred_perf_r2,pred_perf_pval,page_zscore,	
                                                                  page_effect_size,	page_P,	page_var_g,	ukbb_zscore,
                                                                  ukbb_effect_size,	ukbb_pvalue,	ukbb_var_g,
                                                                  PAGE_PP.H4.abf,ukbb_PP.H4.abf) %>%
  mutate(train_pop=if_else(train_pop=="CAU","EUR",train_pop)) %>% separate(gene,into=c("SomaId","gene")) 

s7<-supplemental_table %>%
  inner_join(soma_uniprot_map,by=c("SomaId"))

fwrite(s7,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_SPrediXcan hits.csv")

top_hits<-supplemental_table %>% 
  filter(PAGE_PP.H4.abf > 0.5, replicated==T,model %in% c("baseline","0.001_T")) %>%
  group_by(gene,Phenotype) %>%
  slice_min(n=1,page_P)

strict_top_hits<-supplemental_table %>% 
  filter(PAGE_PP.H4.abf > 0.5, ukbb_PP.H4.abf > 0.5, replicated==T,model %in% c("baseline","0.001_T"))
table(strict_top_hits$model)
```

```{r}
PAV_filtered_results<-fread("Z:/scratch/TOPMed_Proteome/08PWAS/PAGE_bonf_signif/PAGE_PCAIR_baseline_PAV_adjusted_all_results_S-Pred_hits.csv") %>% 
  select(gene,phenotype,train_pop,zscore,effect_size,pred_perf_r2,pred_perf_pval,pvalue) %>%
  mutate(gene=gsub("\\.[0-9]+","",gene)) %>%
  rename(pav_adj_effect="effect_size",pav_adj_pvalue="pvalue",pav_adj_pred_perf_r2="pred_perf_r2",pav_adj_pred_perf_pval="pred_perf_pval")
PAV_filtered_results<-PAV_filtered_results %>% mutate(pav_bonf=0.05/nrow(PAV_filtered_results))


page_results_PAV_adj<-page_bonf_colocalized_ukbb_strict %>% inner_join(PAV_filtered_results,by=c("gene","Phenotype"="phenotype","train_pop"))


# how many distinct associations are there in  page
page_bonf_colocalized_ukbb_strict %>% filter(model %in% c("baseline")) %>% select(gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()
#how many of those associations are still present when doing pav adjustment
page_results_PAV_adj %>% filter(model %in% c("baseline")) %>% filter(pav_adj_pvalue < pav_bonf) %>% select(gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()

#how many distinct associations are also colocalized and replicate in UKBB
page_bonf_colocalized_ukbb_strict %>% 
  filter(PAGE_PP.H4.abf > 0.5,sign(page_zscore) == sign(ukbb_zscore) , ukbb_pvalue < ukbb_bonf_thresh,model %in% c("baseline")) %>% select(gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()
#how many distinct associations are also colocalized and replicate in UKBB after adjusting for pavs
page_results_PAV_adj  %>% 
  filter(PAGE_PP.H4.abf > 0.5,sign(page_zscore) == sign(ukbb_zscore) , ukbb_pvalue < ukbb_bonf_thresh,model %in% c("baseline"),pav_adj_pvalue < pav_bonf) %>% select(gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()

page_results_PAV_adj<-page_bonf_colocalized_ukbb_strict %>% left_join(PAV_filtered_results,by=c("gene","Phenotype"="phenotype","train_pop")) %>%
  separate(gene,into=c("SomaId","gene")) %>%
  inner_join(soma_uniprot_map,by=c("SomaId"))

#add n PAVs to table




fwrite(page_results_PAV_adj,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results.csv")
```


append nPAV to table

```{r}
table<-fread("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results.csv")
db_dir<-"Z:/scratch/TOPMed_Proteome/06Elastic_net/PAV_modeling/db_out/"
dbs<-list.files(db_dir,"*unfiltered.db")
db_list<-vector(mode="list",length(dbs))
driver <- dbDriver('SQLite')
for( i in 1:length(dbs)){
  con<-dbConnect(driver,db_dir %&% dbs[i])
  db_list[[i]]<-dbReadTable(con,"extra") %>% select(gene,n_PAVs_found,pred.perf.R2,pred.perf.pval) %>% mutate(source=dbs[i])
}
db_df<-bind_rows(db_list) %>% separate(gene,into=c("SomaId","gene")) %>%
  mutate(train_pop=substr(source,1,3)) %>% select(-source)
res_with_n_PAV<-left_join(table,db_df,by=c("SomaId","gene","train_pop")) %>%
  mutate(pav_adj_pred_perf_r2=pred.perf.R2,pav_adj_pred_perf_pval=pred.perf.pval) %>% select(-pred.perf.R2,-pred.perf.pval)
fwrite(res_with_n_PAV,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results.csv")
```


```{r}
db_dir<-"Z:/scratch/TOPMed_Proteome/investigate_APOE/model_PAV_adj_APOE/db/"
dbs<-list.files(db_dir,"*unfiltered.db")
db_list<-vector(mode="list",length(dbs))
driver <- dbDriver('SQLite')
for( i in 1:length(dbs)){
  con<-dbConnect(driver,db_dir %&% dbs[i])
  db_list[[i]]<-dbReadTable(con,"extra") %>% select(gene,pred.perf.R2,pred.perf.pval,n_PAVs_found) %>% mutate(source=dbs[i])
}
db_df<-bind_rows(db_list) %>% separate(gene,into=c("SomaId","gene")) %>%
  mutate(train_pop=substr(source,1,3)) %>% select(-source)

```

```{r}
apoe_page_dir<-"Z:/scratch/TOPMed_Proteome/investigate_APOE/PAGE_spred/"
apoe_page_files<-list.files(apoe_page_dir)
apoe_page_list<-vector(mode="list",length(apoe_page_files))
for (i in 1:length(apoe_page_files)){
  apoe_page_list[[i]]<-fread(apoe_page_dir %&% apoe_page_files[i]) %>% mutate(source=apoe_page_files[i])
}
apoe_page_list<-apoe_page_list[sapply(apoe_page_list, nrow) > 0]
apoe_page_df<-bind_rows(apoe_page_list) %>% 
  separate(gene,into=c("SomaId","gene"),sep="_") %>% 
  mutate(phenotype=gsub("_[A-Z]+_APOE_PAV_adj\\.csv","",source),
         train_pop=str_remove(source,phenotype %&% "_"),
         train_pop=substr(train_pop,1,3),
         gene=gsub("\\.[0-9]+","",gene)) %>% 
  select(SomaId,gene,train_pop,phenotype,zscore,effect_size,pvalue) %>%
  rename_with(.fn=function(x){paste0("APOE_adj_",x)})
#db_df<-bind_rows(db_list) %>% separate(gene,into=c("SomaId","gene")) %>% mutate(train_pop=substr(source,1,3)) %>% select(-source)
```

```{r }

append_APOE_results<-left_join(res_with_n_PAV,db_df,by=c("SomaId","gene","train_pop")) %>% left_join(apoe_page_df,by=c("SomaId"="APOE_adj_SomaId","gene"="APOE_adj_gene","train_pop"="APOE_adj_train_pop","Phenotype"="APOE_adj_phenotype"))
# fwrite(res_with_n_PAV,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Wheeler lab\\full_annotated_protein_results_nPAV_apoe_results.csv")
fwrite(append_APOE_results,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results_nPAV_apoe_results.csv")
```


```{r}
annotated_results<-fread("Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results_nPAV_apoe_results.csv")
db_df<-rename(db_df,apoe_n_pav="n_PAVs_found")
annotated_results<-annotated_results %>% left_join(db_df,by=c("SomaId","gene","train_pop","pred.perf.R2","pred.perf.pval"))
annotated_results<-annotated_results %>%
  mutate(actual_adjusted_pval=if_else(EntrezGeneSymbol=="APOE",APOE_adj_pvalue,pav_adj_pvalue),
         actual_adjusted_effect_size=if_else(EntrezGeneSymbol=="APOE",APOE_adj_effect_size,pav_adj_effect),
         actual_adjusted_zscore=if_else(EntrezGeneSymbol=="APOE",APOE_adj_zscore,zscore),
         actual_adjusted_pred_perf_r2=if_else(EntrezGeneSymbol=="APOE",pred.perf.R2,pav_adj_pred_perf_r2),
         actual_adjusted_pred_perf_pval=if_else(EntrezGeneSymbol=="APOE",pred.perf.pval,pav_adj_pred_perf_pval),
         actual_nPAV=if_else(EntrezGeneSymbol=="APOE",apoe_n_pav,n_PAVs_found))
fwrite(annotated_results,"Z:/scratch/TOPMed_Proteome/figures_and_tables/final_figures_and_tables/figures_and_tables/full_annotated_protein_results_nPAV_actual.csv")
```

## summarise

how many distinct bonferonni hits were there in baseline?
how many distinct hits are the same between baseline and pav adjusted baseline?
how many of our "gold standard" hits are still bonferroni significant after pav adjustment?

```{r}
#how many distinct bonferonni hits were there in baseline?
baseline_results %>% select(SomaId,gene,Phenotype) %>% arrange() %>% distinct() %>% nrow() 

#how many distinct hits are the same between baseline and pav adjusted baseline?  Accounting for APOE
baseline_results <-mutate(baseline_results,actual_adjusted_pval=if_else(EntrezGeneSymbol=="APOE",APOE_adj_pvalue,pav_adj_pvalue))
baseline_results %>% filter(pav_adj_pvalue < page_bonf_thresh) %>% select(SomaId,gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()  
baseline_results %>% filter(actual_adjusted_pval < page_bonf_thresh) %>% select(SomaId,gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()

#how many of our "gold standard" hits are still bonferroni significant after pav adjustment?
gold_standard<-baseline_results %>% filter(ukbb_pvalue < ukbb_bonf_thresh, sign(page_zscore) == sign(ukbb_zscore), PAGE_PP.H4.abf > 0.5)
gold_standard %>% select(SomaId,gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()  
gold_standard %>% filter(pav_adj_pvalue < page_bonf_thresh) %>% select(SomaId,gene,Phenotype) %>% arrange() %>% distinct() %>% nrow()  
gold_standard %>% filter(actual_adjusted_pval < page_bonf_thresh) %>% select(Target,gene,Phenotype) %>% arrange() %>% distinct() 
```
